Modeling vertical-axis cross-flow turbine wakes

### 2015-07-22 paper.tex
Fix unit abbreviation
Write about the modeling challenge

@@

Timestep dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:timestep-dep}. It was seen that the
Spalart--Allmaras model converged well with decreasing timestep, leading to a
final timestep of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002 s$, which was the final timestep chosen to run the
simulations.

>>>>

Modeling the boundary layer flows on cross-flow turbine blades is very
challenging due to the dynamically changing inflow and angle of attack---which
often exceeds static stall values and causes dynamic stall. Furthermore, the
ability to predict the occurrence and interdependence of boundary layer
transition and separation can have dramatic influence on the blade loading and
therefore the predicted turbine power output.

@@

Timestep dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:timestep-dep}. It was seen that the
Spalart--Allmaras model converged well with decreasing timestep, leading to a
final timestep of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002$ s, which was the final timestep chosen to run the
simulations.
